---
title: "Exploring R Graphics"
output: html_notebook
---

Github repository: https://github.com/nohturfft/RES602_2020  


Useful resource:  
An excellent resource for learning to generate graphics in R is the "[R Graphics Cookbook](https://r-graphics.org/)" by Winston Chang, which is freely available online.

```{r}
if (! requireNamespace("ggplot2")) install.packages("ggplot2")
library(ggplot2)
```


Base R comes with a number of built-in datasets that are useful to try out code, especially to develop graphics.  
In order to see a list of available datasets use the `help()` function as shown below:  
```{r}
help(package="datasets")
```


## Scatterplot  
```{r}
iris.data <- iris
head(iris.data)
```


```{r}
gg1 <- ggplot(iris.data, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) +
  geom_point()
gg1
```

```{r}
gg2 <- ggplot(iris.data, aes(x=Petal.Length, y=Petal.Width, color=Species)) +
  geom_point()
gg2
```


```{r}
gg3 <- ggplot(iris.data, aes(x=Sepal.Length, y=Petal.Length, color=Species)) +
  geom_point() +
  stat_smooth(method = lm, level = 0.99)
gg3
```

Practise scatterplot: BMS_1920_Marks.xlsx  


## Line graphs  
Using base R:  
```{r}
p <- pressure
# dim(p) # 19 2
plot(pressure$temperature, pressure$pressure, type = "l")
```

Using ggplot2:  
```{r}
ggplot(pressure, aes(x = temperature, y = pressure)) +
  geom_line()
```

```{r}
ggplot(pressure, aes(x = temperature, y = pressure)) +
  geom_line() +
  geom_point()
```

## Bar graphs  
```{r}
help(BOD, package="datasets")
b1 <- BOD
ggplot(b1, aes(x = factor(Time), y = demand)) +
  geom_col()
```

```{r}
# head(mtcars)
b2 <- table(mtcars$cyl) %>% as.data.frame() %>% set_colnames(c("Cylinders", "Count"))
ggplot(b2, aes(x = Cylinders, y = Count)) +
  geom_col()
```

## Histogram  
```{r}
hist(mtcars$mpg, breaks = 10)
```

```{r}
ggplot(mtcars, aes(x = mpg)) +
  geom_histogram()
```

Practise histograms: BMS_1920_Marks.xlsx

## Box-and-whisker plot  
```{r}
boxplot(len ~ supp, data = ToothGrowth)
```

```{r}
ggplot(ToothGrowth, aes(x = supp, y = len)) +
  geom_boxplot()
```

